MP MetaAnalysis

### 2018-01-24 Analyses.Rmd
commit dataset, figures, write-ups

#Because we do hierarchical models, we do not collapse. This is better when looking at an interaction effect.

@@

```
The next table shows what type of publications were included in our meta-analysis
```{r DescriptivesPubtype, echo = FALSE}

@@

```{r LanguageEffectAnalyses}
dat$condition_label = ifelse(dat$condition==1, "correct", "MP")

@@

```
We have 17 correlations, roughly evenly divided between comprehension and production data. There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we should both analyze this data separately and see whether it makes sense in a joint analysis.

@@

# Plotting
## Mispronunciation Effect by Age (color)
```{r PlotMPEffect}

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g),show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  theme_bw()+
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

>>>>

@@

@@

```{r LanguageEffectAnalyses}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

@@

We have 17 correlations, roughly evenly divided between comprehension and production data. There is reason to believe that production data are different from comprehension data (the former being easier to estimate for parents in the typical questionnaire-based assessment), so we should both analyze this data separately and see whether it makes sense in a joint analysis.

@@

# Plotting
```{r PlotAPATheme}
#Themes and plot
apatheme=theme_bw()+
  theme(#panel.grid.major=element_blank(),
    #panel.grid.minor=element_blank(),
    #panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

```
## Mispronunciation Effect by Age (color)
```{r PlotMPEffect}

dat$condition_label = ifelse(dat$condition==1, "Correct", "Mispronunciation")

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  geom_point(aes(size = weights_g),show.legend=FALSE) + 
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
